---
title: "The Political Economy of Higher Education: Preferences, Inequality, and Policy Change"
subtitle: "Dissertationskolloquium"
date: "13. Mai 2022"
author: Timm Fulge
bibliography: bib/mybib.bib
output:
  beamer_presentation:
    theme: BIGSSS
    fonttheme: professionalfonts
    slide_level: 2
header-includes:
  - \AtBeginEnvironment{CSLReferences}{\tiny} # small font size in references section
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Einstieg {.build}

```{r, fig.cap = "Enrolment Ratios in 1997 and 2016",echo = F,warning = F, message = F, out.height= "8cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```


## dfjkdjflkdj {.build}

\begin{columns}
\column{0.66\textwidth}
```{r, fig.cap = "Enrolment Ratios in 1997 and 2016",echo = F,warning = F, message = F, out.height= "6cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```
\column{0.33\textwidth}
\begin{itemize}
\item{test}
\end{itemize}
\end{columns}

## Einstieg {.build}

Ist es möglich, einen Umlaut zu zeigen?

This article was written by @Ansell.2008b.

The same author has supporting evidence [@Ansell.2013].

Another argument was advanced by Garritzmann [-@garritzmann2016]

Does Markdown automatically expand on the references section [@Pierson.1993; @Hall.1996; @Hall.2001]?

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r, fig.cap = "Illustration of higher education system ideal types",echo = F,warning = F, message = F, out.height= "4cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```

- What happens if I put stuff here?

- Doesn't seem to automatically resize the plot

## Next slide with plot

```{r}
plot(pressure)
```
- Is he willing to do what I want here?

- By which I mean automatically resizing the image at hand

- He doesnt, not even now?


## Two column layout

\footnotesize
:::::::::::::: {.columns}
::: {.column}
```{r, fig.cap = "Illustration of higher education system ideal types",echo = F,warning = F, message = F, out.height= "4cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```
:::
::: {.column}
- This text is meant to describe the picture shown on the left. Got it?
:::
::::::::::::::

## Final Test

Blocks

\begin{alertblock}{Theses}
1. The world is round \newline
2. It goes around
\end{alertblock}

## References {.allowframebreaks}
