---
title: "The Political Economy of Higher Education: Preferences, Inequality, and Policy Change"
subtitle: "Dissertationskolloquium"
date: "13. Mai 2022"
author: Timm Fulge
bibliography: bib/mybib.bib
output:
  beamer_presentation:
    theme: BIGSSS
    fonttheme: professionalfonts
    slide_level: 2
header-includes:
  - \AtBeginEnvironment{CSLReferences}{\tiny} # small font size in references section
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) 

library(tidyverse)

```

## Einstieg {.build}

```{r, fig.cap = "Enrolment Ratios in 1997 and 2016",echo = F,warning = F, message = F, fig.height= 4}

read.csv("Figures/OUP_enrol_MF_v1.csv") -> base.data

base.data %>% 
  filter(year > 1945, sex == "MF", region_code == "Advanced Economies", country != "Luxembourg") %>% 
  mutate(color = case_when(country == "Germany" ~ "Germany",
                           country == "USA" ~ "United States",
                           country == "United Kingdom" ~ "United Kingdom",
                           country == "Switzerland" ~ "Switzerland",
                           country == "Finland" ~ "Finland",
                           country == "Sweden" ~ "Sweden",
                          TRUE ~ NA_character_)) %>% 
  ggplot(aes(x = year, y = ter, group = country)) +
  geom_line(alpha = 0.5) +
  geom_line(data = . %>% filter(!is.na(color)),
            aes(x = year, y = ter, group = country, color = color),
            size = 1.5)


```


## dfjkdjflkdj 

\begin{columns}
\column{0.66\textwidth}
```{r, fig.cap = "Enrolment Ratios in 1997 and 2016",echo = F,warning = F, message = F, out.height= "6cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```
\column{0.33\textwidth}

Hier wird Text eingebracht \newline
\begin{itemize}[<+->]
\item{test 1 2 3}
\item{test 3 4 5}
\begin{itemize}
\item{mano a mano}
\end{itemize}
\end{itemize}

> - Eat eggs
> - Drink coffee
>    - Have at it

\end{columns}

## Einstieg 

Ist es möglich, einen Umlaut zu zeigen?

This article was written by @Ansell.2008b.

The same author has supporting evidence [@Ansell.2013].

Another argument was advanced by Garritzmann [-@garritzmann2016]

Does Markdown automatically expand on the references section [@Pierson.1993; @Hall.1996; @Hall.2001]?

## Slide with (incremental) Bullets

> - Eat eggs
> - Drink coffee
>    - Have at it

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r, fig.cap = "Illustration of higher education system ideal types",echo = F,warning = F, message = F, out.height= "4cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```

- What happens if I put stuff here?

- Doesn't seem to automatically resize the plot

## Next slide with plot

```{r}
plot(pressure)
```
- Is he willing to do what I want here?

- By which I mean automatically resizing the image at hand

- He doesnt, not even now?


## Two column layout

\footnotesize
:::::::::::::: {.columns}
::: {.column}
```{r, fig.cap = "Illustration of higher education system ideal types",echo = F,warning = F, message = F, out.height= "4cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```
:::
::: {.column}
> - Eat eggs
> - Drink coffee
>    - Have at it
:::
::::::::::::::

## Final Test

Blocks

\begin{alertblock}{Theses}
1. The world is round \newline
2. It goes around
\end{alertblock}

## References {.allowframebreaks}
