---
title: "The Political Economy of Higher Education: Preferences, Inequality, and Policy Change"
subtitle: "Dissertationskolloquium"
date: "13. Mai 2022"
author: Timm Fulge
bibliography: bib/mybib.bib
output:
  beamer_presentation:
    theme: BIGSSS
    fonttheme: professionalfonts
    slide_level: 2
header-includes:
  - \AtBeginEnvironment{CSLReferences}{\tiny} # small font size in references section
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) 


```

## Einstieg 

```{r, fig.cap = "Enrolment in Secondary and Higher Education, Developed Countries, 1950-2010",echo = F,warning = F, message = F}

knitr::include_graphics("Figures/FiguresEnrolment_over_time_new-1.pdf")

```
\pause

\begin{itemize}
\item{Genereller Trend zur Expansion}
\item{Hochschulbildung: Bemerkenswerte Varianz zwischen einzelnen Ländern (nicht nur in Bezug auf Enrolment)}
\end{itemize}

## Einstieg 

Higher Education is special!

\pause

\begin{alertblock}{Leitfragen}
\begin{itemize}[<+->]
\item{Wie können Hochschulsysteme möglichst ganzheitlich konzeptualisiert werden?}
\item{Welche Varianz zeigt sich zwischen Ländern sowie über die Zeit?}
\item{Welche (re)distributiven Implikationen haben unterschiedliche Designs von Hochschulsystemen?}
\item{Wie können Unterschiede erklärt werden?}
\begin{itemize}
\item{Sozio-ökonomischer Problemdruck}
\item{Pfadabhängigkeiten}
\item{Parteipolitik}
\end{itemize}
\end{itemize}
\end{alertblock}

## Einstieg

**Kumulative Dissertation**, auf Englisch verfasst und bestehend Introduction und drei Einzelarbeiten in alleiniger Autorenschaft:

\begin{itemize}
\item{\textit{The Trilemma of Higher Education and Equality of Opportunity: Social Background, Access to Higher Education and the Moderating Impact of Enrolment and Public Subsidization}}
\item{\textit{Explaining Institutional Change in UK Higher Education: Towards A Partisan Theory?}}
\item{\textit{The Role of Parties in the Distributive Politics of Higher Education}}
\end{itemize}

## Stand der Forschung

```{r, fig.cap = "Evolution der Literatur zum Forschungsgegenstand",echo = F,warning = F, message = F}
knitr::include_graphics("Figures/Intro/EvolutionOfTheField.drawio.pdf")
```

## dfjkdjflkdj 

\begin{columns}
\column{0.66\textwidth}
```{r, fig.cap = "Evolution der Literatir",echo = F,warning = F, message = F, out.height= "6cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```
\column{0.33\textwidth}

Hier wird Text eingebracht \newline
\begin{itemize}[<+->]
\item{test 1 2 3}
\item{test 3 4 5}
\begin{itemize}
\item{mano a mano}
\end{itemize}
\end{itemize}

> - Eat eggs
> - Drink coffee
>    - Have at it

\end{columns}

## Einstieg 

Ist es möglich, einen Umlaut zu zeigen?

This article was written by @Ansell.2008b.

The same author has supporting evidence [@Ansell.2013].

Another argument was advanced by Garritzmann [-@garritzmann2016]

Does Markdown automatically expand on the references section [@Pierson.1993; @Hall.1996; @Hall.2001]?

## Slide with (incremental) Bullets

> - Eat eggs
> - Drink coffee
>    - Have at it

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r, fig.cap = "Illustration of higher education system ideal types",echo = F,warning = F, message = F, out.height= "4cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```

- What happens if I put stuff here?

- Doesn't seem to automatically resize the plot

## Next slide with plot

```{r}
plot(pressure)
```
- Is he willing to do what I want here?

- By which I mean automatically resizing the image at hand

- He doesnt, not even now?


## Two column layout

\footnotesize
:::::::::::::: {.columns}
::: {.column}
```{r, fig.cap = "Illustration of higher education system ideal types",echo = F,warning = F, message = F, out.height= "4cm"}
knitr::include_graphics("Figures/Intro/Enrolment_over_time-1.pdf")
```
:::
::: {.column}
> - Eat eggs
> - Drink coffee
>    - Have at it
:::
::::::::::::::

## Final Test

Blocks

\begin{alertblock}{Theses}
1. The world is round \newline
2. It goes around
\end{alertblock}

## Referenzen {.allowframebreaks}
